Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-31 ms.tex
fixed results nightmare

Figure~\ref{fig:stag} shows our calculation of the stagnation radius $r_{\rm s}/r_{\rm
  soi}$, with different colors showing different values of $v_{w}$.
Cusp and core galaxies are marked with square and triangles,
respectively.  Shown for comparison are our analytic results
(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
galaxies, respectively, calculated assuming $\densSlope = 1$ and
$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).

Our analytic estimates accurately reproduce the numerical results in the high heating limit $v_{\rm w} \gg
\sigma_0$ ($r_{\rm s} \lesssim r_{\rm soi}$).  However, for sufficiently low $v_{\rm w}/\sigma_0$ the stagnation radius exceeds the analytic estimate, approaching the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence occurs approximately when $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix \ref{app:be}), and hence occurs at a higher value of $v_w/\sigma_0$ in the case of a core galaxies ($\Gamma = 0.8$) with large break radii.  This behavior explains the three core galaxies shown as green squares, which are vertically aligned at the same value of $v_{w}/\sigma$ (close to where the analytic estimate diverges) correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).

>>>>

Figure~\ref{fig:stag} shows our calculation of the stagnation radius $r_{\rm s}/r_{\rm
  soi}$ as a function of the wind heating parameter $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0$, with different colors showing different values of $v_{w}$.  Cusp and core galaxies are marked with square and triangles,
respectively.  Shown for comparison are our analytic results
(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
galaxies, respectively, calculated assuming $\densSlope = 1$ and
$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).

Our analytic estimates accurately reproduce the numerical results in the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s} \lesssim r_{\rm soi}$).  However, for sufficiently low heating the stagnation radius diverges above the analytic estimate, approaching the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence occurs approximately when $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix \ref{app:be}), and hence occurs at a higher value of $\zeta$ in the case of core galaxies ($\Gamma = 0.8$) with large break radii.  This behavior explains the three core galaxies shown as green squares, which are vertically aligned at the same value of $\zeta$ close to where the analytic estimate diverges; these correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom) corresponding to successively larger values of $\zeta_c$.
